---
title: "HomeCOG Batch1 PerfO Report 12-12"
output: 
  html_document:
    code_folding: hide

---

Coding for weekly audit of HomeCog Batch 1 data collection. The purpose of this document is to structure what will be circulated and reviewed by the HoPE Aim 1 team on a weekly basis.   
  
  
To-Do for Dec 12th:  
-Performance Outcome stuff. 
---Means (Done!, hist and datatable). 
---IIC (Done!, hist and table<- make datatable?). 
---response times (Done! datatable). 
---summary by descriptives (DTF/DIF, add in additional descriptives). 
---missing data (Done!, datatable). 

```{r setup, include=FALSE}
#install.packages("data.table")
library(data.table)
#install.packages("DT")
library(DT)

knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

## **Loading Data:**
```{r loadExcel}
setwd( "/Users/chapm564/Documents/GitHub/HomeCog_Batch1_Weekly_Reports")

#Item Text
item_text=read.csv("Batch_1_Item_Text.csv")

#HoPE Calibration Recruitment
Recruitment=read.delim("HoPe Calibration Recruitment.txt",sep="\t")
names(Recruitment)[names(Recruitment)=="Participant.ID"]="Recruitment_id"
names(Recruitment)[names(Recruitment)=="FastTest.ID"]="Test.Code"
names(Recruitment)[names(Recruitment)=="Age"]="Recruitment_age"
names(Recruitment)[names(Recruitment)=="Sex"]="Recruitment_gender"

#REDCap data
REDCap=read.csv("ProjectHoPeCalibrati_DATA_2023-12-08_0913.csv")
names(REDCap)[names(REDCap)=="record_id"]="REDCap_id"
names(REDCap)[names(REDCap)=="fasttest"]="Test.Code"
names(REDCap)[names(REDCap)=="enrollment_date"]="REDCap_date"
names(REDCap)[names(REDCap)=="age"]="REDCap_age"
names(REDCap)[names(REDCap)=="gender"]="REDCap_gender"
REDCap$REDCap_gender[REDCap$REDCap_gender==1]="F"
REDCap$REDCap_gender[REDCap$REDCap_gender==2]="M"
# 
REDCap$REDCap_date=strftime(REDCap$REDCap_date, "%m/%d/%Y")


# record_id	<- REDCap ID- rename
# enrollment <- 1/0? maybe remove if not 1
# enrollment_date <- date of adminsitration, check against FastTest date
# fasttest <- merge
# age <- check against Recruitment spreadsheet
# gender <- check against Recruitment spreadsheet
# interest <- PHQ2?
# feeling <- PHQ2?
# within_year <- SDOH questions answered within a year
# alcohol <- SDOH1
# dentist <- SDOH2
# employment <- SDOH3
# inactive <- SDOH3a
# active <- SDOH3b
# olive_oil <- SDOH4
# exercise <- SDOH5
# minutes <- SDOH6
# telephone <- SDOH7
# transportation <- SDOH8
# basics <- ????
# who <- Description of who's answering CareGiving questions below 
# return_you <- CG1a
# return_care <- CG1b
# help_you <- CG2a
# help_care <- CG2b
# hours_you <- CG3a
# hours_care <- CG3b
# limit_care <- CG4
# yes___1 <- CG4a
# yes___2 <- CG4b
# limit_you <- CG5
# yes_you___1 <- CG5a
# yes_you___2 <- CG5b
# comfort_you <- CG6a
# comfort_care <- CG6b
# meds_you <- CG7a
# meds_care <- CG7b
# form_1_complete <- ????


#Read in FastTest Raw Response Data
FastTest=read.csv("ExamineeResponses-12-19-2023-8-59-11.csv", skip = 1, stringsAsFactors = TRUE)
FastTest=FastTest[FastTest$Test=="Batch_1",]
#Remove variables that will be unused for analyses
FastTest=FastTest[,!(names(FastTest) %in% c("Test.Code.Email.s.","Test.Results.Email.s.","External.ID","SE","Passed"))]
#relabel date as FastTest date
names(FastTest)[names(FastTest)=="Date"]="FastTest_date"
FastTest$Test.Code=as.character(FastTest$Test.Code)

#Relabel variables from FAMCAT with "FAMCAT_" prefix
FAMCAT=grep("^X[0-9]+[0-9]+[0-9]", names(FastTest))
names(FastTest)[FAMCAT]=gsub("X","FAMCAT_",names(FastTest)[FAMCAT])

#Relabel variables from HoPE Batch 1 PRO items with "HoPE_PRO_" prefix
HoPE_PRO=grep("^X[0-9]+[0-9]|^X[0-9]", names(FastTest), value=TRUE)
names(FastTest)[names(FastTest) %in% HoPE_PRO]=gsub("X","HoPE_PRO_",names(FastTest)[names(FastTest) %in% HoPE_PRO])
HoPE_PRO=gsub("X","HoPE_PRO_",HoPE_PRO)

#Relabel variables from HoPE Batch 1 PerfO items with "HoPE_PerfO_" prefix
HoPE_PerfO=grep("^Memory_|^Naming_|^Semantic_Assoc_|^Comprehension_|^Vigilance_|^Abstraction_|^Sequencing_|^ZChI|^Cc5g|^Uu16|^Arithmetic_|^Clock_|^VisuoPerc_|^VisuoSpatial_" , names(FastTest), value=TRUE)
names(FastTest)[names(FastTest) %in% HoPE_PerfO]=paste0("HoPE_PerfO_",names(FastTest)[names(FastTest) %in% HoPE_PerfO])
HoPE_PerfO=paste0("HoPE_PerfO_",HoPE_PerfO)

#Reduce Batch 1 PRO 'item text' table to only those items administered in Batch 1 (36 items)
item_text=item_text[item_text$Item_Number %in% gsub("HoPE_PRO_","",HoPE_PRO),]

###############################
### load in FAMCAT Scale Scores
###############################

FastTest2=read.csv("ExamineeData-12-19-2023-8-59-01.csv")
FastTest2=FastTest2[FastTest2$Test=="Male"|FastTest2$Test=="Female"& !is.na(FastTest2$First.Name),]


###############################
### load in FAMCAT Scale Scores
###############################

ResponseTimes=read.csv("ItemTimes-12-19-2023-8-59-21.csv")

ResponseTimes=ResponseTimes[ResponseTimes$Test=="Batch_1",]
#Remove variables that will be unused for analyses
ResponseTimes=ResponseTimes[,!(names(ResponseTimes) %in% c("Test.Code.Email.s.","Test.Results.Email.s.","External.ID","SE","Passed"))]
#relabel date as FastTest date
names(ResponseTimes)[names(ResponseTimes)=="Date"]="FastTest_date"

#Relabel variables from FAMCAT with "FAMCAT_" prefix
FAMCATxnames=grep("^X[0-9]+[0-9]+[0-9]", names(ResponseTimes))
names(ResponseTimes)[FAMCATxnames]=gsub("X","FAMCAT_",names(ResponseTimes)[FAMCATxnames])

#Relabel variables from HoPE Batch 1 PRO items with "HoPE_PRO_" prefix
HoPE_PROxnames=grep("^X[0-9]+[0-9]|^X[0-9]", names(ResponseTimes), value=TRUE)
names(ResponseTimes)[names(ResponseTimes) %in% HoPE_PROxnames]=gsub("X","HoPE_PRO_",names(ResponseTimes)[names(ResponseTimes) %in% HoPE_PROxnames])


#Relabel variables from HoPE Batch 1 PerfO items with "HoPE_PerfO_" prefix
HoPE_PerfOxnames=grep("^Memory_|^Naming_|^Semantic_Assoc_|^Comprehension_|^Vigilance_|^Abstraction_|^Sequencing_|^ZChI|^Cc5g|^Uu16|^Arithmetic_|^Clock_|^VisuoPerc_|^VisuoSpatial_" , names(ResponseTimes), value=TRUE)
names(ResponseTimes)[names(ResponseTimes) %in% HoPE_PerfOxnames]=paste0("HoPE_PerfO_",names(ResponseTimes)[names(ResponseTimes) %in% HoPE_PerfOxnames])

```

```{r DataLinking}
#Adjustments to be relayed to coordinators 
REDCap[REDCap$Test.Code=="MIH-090-764-944", "REDCap_date"]="11/30/2023"
REDCap[REDCap$Test.Code=="ECO-622-460-859", "REDCap_gender"]="F"
FastTest=FastTest[!(FastTest$Test.Code %in% c("CBU-218-600-873","NYS-954-156-833")),]
FastTest2=FastTest2[!(FastTest2$Test.Code %in% c("CBU-218-600-873","NYS-954-156-833")),]


# Administration Date Linking
MergeCheck=merge(FastTest, REDCap, by="Test.Code")
if(length(which(MergeCheck$FastTest_date != MergeCheck$REDCap_date))==0){
    names(FastTest)[names(FastTest)=="FastTest_date"]="Date"
    names(REDCap)[names(REDCap)=="REDCap_date"]="Date"
}else{print(paste("DATE MISMATCH: FastTest & REDCap"))}

# ID Linking
MergeCheck=merge(Recruitment, REDCap, by="Test.Code")
if(length(which(MergeCheck$Recruitment_id != MergeCheck$REDCap_id))==0){
    names(Recruitment)[names(Recruitment)=="Recruitment_id"]="ID"
    names(REDCap)[names(REDCap)=="REDCap_id"]="ID"
  }else{print("ID MISMATCH: Recruitment & REDCap")}

# Age
if(length(which(as.numeric(gsub("-year old", "",MergeCheck$Recruitment_age)) != MergeCheck$REDCap_age))==0){
    names(Recruitment)[names(Recruitment)=="Recruitment_id"]="ID"
    names(REDCap)[names(REDCap)=="REDCap_id"]="ID"
  }else{print("AGE MISMATCH: Recruitment & REDCap")}

# Gender
if(length(which(MergeCheck$Recruitment_gender != MergeCheck$REDCap_gender))==0){
    names(Recruitment)[names(Recruitment)=="Recruitment_gender"]="Gender"
    names(REDCap)[names(REDCap)=="REDCap_gender"]="Gender"
  }else{print("GENDER MISMATCH: Recruitment & REDCap")}


###############################################
### Merge #####################################
###############################################
#Merge together FastTest Batch 1 and FastTest Non-Porch FAMCAT
data=merge(by = "Test.Code", all.x=TRUE,
  x=FastTest,
  y=FastTest2[,c("Test.Code",sapply(c("APPLIED_COGNITION","DAILY_ACTIVITIES","MOBILITY"), paste0, c("_SCORE","_SEM")))])
#Merge together FastTest (Batch1 & FAMCAT NonPorch) with Recruitment data
data=merge(by = "Test.Code", all.x=TRUE,
  x=data,
  y=Recruitment)
#Merge together FastTest (Batch1 & FAMCAT NonPorch) & Recruitment data with REDCap data
data=merge(by = "Test.Code", all.x=TRUE,
  x=data,
  y=REDCap)


```


------------------------------------------------------------------------------------------------------

## **Data Cleaning.** 
  
### 0. Data recoding.  
```{r Recoding, results='hide'}

#####Recruitment

#need to reduce down the dataset to just the folks with FastTest data or just those with data for recruitment

#Gender
table(Recruitment$Recruitment_gender)
#Race <- 15 folks missing or ""
table(Recruitment$Race)
#Ethnicity <- 15 folks missing or ""
table(Recruitment$Ethnicity)
#Age 
Recruitment$Age=as.numeric(gsub("-year old","",Recruitment$Recruitment_age))
table(Recruitment$Age)
#Age bands (<65 & >=65)
Recruitment$AgeBands=as.character(cut(Recruitment$Age, breaks=c(0,65,120), right=FALSE))
data$REDCap_age=cut(data$REDCap_age, breaks=c(0,65,120), right=FALSE)
#Cognitive impairment
table(Recruitment$Cogn.Impairment)

#HomeCog Status
table(Recruitment$HomeCog.Interrupted....completed..)

#FAMCAT Status
table(Recruitment$FAMCAT.Interrupted....completed..)

#Audio
table(Recruitment$Audio..Good.Bad.)

#Notes
table(Recruitment$Notes)

#Merge recruitment data into FastTest data
data=merge(data, Recruitment, by="Test.Code", all.x=TRUE )



#####FastTest PRO
for(var in HoPE_PRO){
  levels(data[,var])[which(levels(data[,var])=="")]=NA
  
  levels(data[,var])[which(levels(data[,var])=="Very Often")]=1
  levels(data[,var])[which(levels(data[,var])=="Often")]=2
  levels(data[,var])[which(levels(data[,var])=="Sometimes")]=3
  levels(data[,var])[which(levels(data[,var])=="Rarely")]=4
  levels(data[,var])[which(levels(data[,var])=="Never")]=5  
  
  levels(data[,var])[which(levels(data[,var])=="Unable")]=1
  levels(data[,var])[which(levels(data[,var])=="A lot")]=2
  levels(data[,var])[which(levels(data[,var])=="Some")]=3
  levels(data[,var])[which(levels(data[,var])=="A little")]=4  
  levels(data[,var])[which(levels(data[,var])=="None")]=5
  data[,var]=as.numeric(data[,var])
}


#FastTest PerfO

for(var in HoPE_PerfO){data[,var]=as.factor(data[,var])}

#Memory
levels(data[,"HoPE_PerfO_Memory_1"])[levels(data[,"HoPE_PerfO_Memory_1"])=="B"]=1
levels(data[,"HoPE_PerfO_Memory_1"])[!levels(data[,"HoPE_PerfO_Memory_1"]) %in% c("","1")]=0
  
levels(data[,"HoPE_PerfO_Memory_2"])[levels(data[,"HoPE_PerfO_Memory_2"])=="A"]=1
levels(data[,"HoPE_PerfO_Memory_2"])[!levels(data[,"HoPE_PerfO_Memory_2"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Memory_3"])[levels(data[,"HoPE_PerfO_Memory_3"])=="D"]=1
levels(data[,"HoPE_PerfO_Memory_3"])[!levels(data[,"HoPE_PerfO_Memory_3"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Memory_4"])[levels(data[,"HoPE_PerfO_Memory_4"])=="C"]=1
levels(data[,"HoPE_PerfO_Memory_4"])[!levels(data[,"HoPE_PerfO_Memory_4"]) %in% c("","1")]=0

#Naming
levels(data[,"HoPE_PerfO_Naming_1"])[levels(data[,"HoPE_PerfO_Naming_1"])=="D"]=1
levels(data[,"HoPE_PerfO_Naming_1"])[!levels(data[,"HoPE_PerfO_Naming_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Naming_2"])[levels(data[,"HoPE_PerfO_Naming_2"])=="A"]=1
levels(data[,"HoPE_PerfO_Naming_2"])[!levels(data[,"HoPE_PerfO_Naming_2"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Naming_3"])[levels(data[,"HoPE_PerfO_Naming_3"])=="B"]=1
levels(data[,"HoPE_PerfO_Naming_3"])[!levels(data[,"HoPE_PerfO_Naming_3"]) %in% c("","1")]=0

#Semantic Association
levels(data[,"HoPE_PerfO_Semantic_Assoc_1"])[levels(data[,"HoPE_PerfO_Semantic_Assoc_1"])=="C"]=1
levels(data[,"HoPE_PerfO_Semantic_Assoc_1"])[!levels(data[,"HoPE_PerfO_Semantic_Assoc_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Semantic_Assoc_2"])[levels(data[,"HoPE_PerfO_Semantic_Assoc_2"])=="D"]=1
levels(data[,"HoPE_PerfO_Semantic_Assoc_2"])[!levels(data[,"HoPE_PerfO_Semantic_Assoc_2"]) %in% c("","1")]=0


#Comprehension
levels(data[,"HoPE_PerfO_Comprehension_1"])[levels(data[,"HoPE_PerfO_Comprehension_1"])=="B"]=1
levels(data[,"HoPE_PerfO_Comprehension_1"])[!levels(data[,"HoPE_PerfO_Comprehension_1"]) %in% c("","1")]=0

#Vigilance
levels(data[,"HoPE_PerfO_Vigilance_1"])[levels(data[,"HoPE_PerfO_Vigilance_1"])=="C"]=1
levels(data[,"HoPE_PerfO_Vigilance_1"])[!levels(data[,"HoPE_PerfO_Vigilance_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Vigilance_2"])[levels(data[,"HoPE_PerfO_Vigilance_2"])=="C"]=1
levels(data[,"HoPE_PerfO_Vigilance_2"])[!levels(data[,"HoPE_PerfO_Vigilance_2"]) %in% c("","1")]=0

#Abstraction
levels(data[,"HoPE_PerfO_Abstraction_1"])[levels(data[,"HoPE_PerfO_Abstraction_1"])=="B"]=1
levels(data[,"HoPE_PerfO_Abstraction_1"])[!levels(data[,"HoPE_PerfO_Abstraction_1"]) %in% c("","1")]=0

#Sequencing - this might take some work
levels(data[,"HoPE_PerfO_ZChI"])[levels(data[,"HoPE_PerfO_ZChI"])=="E"]=1
levels(data[,"HoPE_PerfO_ZChI"])[!levels(data[,"HoPE_PerfO_ZChI"]) %in% c("","1")]=0
data[,"HoPE_PerfO_Sequencing_1"]=data[,"HoPE_PerfO_ZChI"]
data=data[,-which(names(data)=="HoPE_PerfO_ZChI")]
HoPE_PerfO=HoPE_PerfO[-which(HoPE_PerfO=="HoPE_PerfO_ZChI")]

levels(data[,"HoPE_PerfO_Cc5g"])[levels(data[,"HoPE_PerfO_Cc5g"])=="20"]=1
levels(data[,"HoPE_PerfO_Cc5g"])[!levels(data[,"HoPE_PerfO_Cc5g"]) %in% c("","1")]=0
data[,"HoPE_PerfO_Sequencing_2"]=data[,"HoPE_PerfO_Cc5g"]
data=data[,-which(names(data)=="HoPE_PerfO_Cc5g")]
HoPE_PerfO=HoPE_PerfO[-which(HoPE_PerfO=="HoPE_PerfO_Cc5g")]

levels(data[,"HoPE_PerfO_Uu16"])[levels(data[,"HoPE_PerfO_Uu16"])=="72"]=1
levels(data[,"HoPE_PerfO_Uu16"])[!levels(data[,"HoPE_PerfO_Uu16"]) %in% c("","1")]=0
data[,"HoPE_PerfO_Sequencing_3"]=data[,"HoPE_PerfO_Uu16"]
data=data[,-which(names(data)=="HoPE_PerfO_Uu16")]
HoPE_PerfO=HoPE_PerfO[-which(HoPE_PerfO=="HoPE_PerfO_Uu16")]

#Arithmetic
levels(data[,"HoPE_PerfO_Arithmetic_1"])[levels(data[,"HoPE_PerfO_Arithmetic_1"])=="A"]=1
levels(data[,"HoPE_PerfO_Arithmetic_1"])[!levels(data[,"HoPE_PerfO_Arithmetic_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_2"])[levels(data[,"HoPE_PerfO_Arithmetic_2"])=="C"]=1
levels(data[,"HoPE_PerfO_Arithmetic_2"])[!levels(data[,"HoPE_PerfO_Arithmetic_2"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_3"])[levels(data[,"HoPE_PerfO_Arithmetic_3"])=="B"]=1
levels(data[,"HoPE_PerfO_Arithmetic_3"])[!levels(data[,"HoPE_PerfO_Arithmetic_3"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_4"])[levels(data[,"HoPE_PerfO_Arithmetic_4"])=="A"]=1
levels(data[,"HoPE_PerfO_Arithmetic_4"])[!levels(data[,"HoPE_PerfO_Arithmetic_4"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_5"])[levels(data[,"HoPE_PerfO_Arithmetic_5"])=="B"]=1
levels(data[,"HoPE_PerfO_Arithmetic_5"])[!levels(data[,"HoPE_PerfO_Arithmetic_5"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_6"])[levels(data[,"HoPE_PerfO_Arithmetic_6"])=="B"]=1
levels(data[,"HoPE_PerfO_Arithmetic_6"])[!levels(data[,"HoPE_PerfO_Arithmetic_6"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_7"])[levels(data[,"HoPE_PerfO_Arithmetic_7"])=="C"]=1
levels(data[,"HoPE_PerfO_Arithmetic_7"])[!levels(data[,"HoPE_PerfO_Arithmetic_7"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_8"])[levels(data[,"HoPE_PerfO_Arithmetic_8"])=="A"]=1
levels(data[,"HoPE_PerfO_Arithmetic_8"])[!levels(data[,"HoPE_PerfO_Arithmetic_8"]) %in% c("","1")]=0

#Clock
levels(data[,"HoPE_PerfO_Clock_1"])[levels(data[,"HoPE_PerfO_Clock_1"])=="A"]=1
levels(data[,"HoPE_PerfO_Clock_1"])[!levels(data[,"HoPE_PerfO_Clock_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Clock_2"])[levels(data[,"HoPE_PerfO_Clock_2"])=="B"]=1
levels(data[,"HoPE_PerfO_Clock_2"])[!levels(data[,"HoPE_PerfO_Clock_2"]) %in% c("","1")]=0

#VisuoPerception
levels(data[,"HoPE_PerfO_VisuoPerc_1"])[levels(data[,"HoPE_PerfO_VisuoPerc_1"])=="D"]=1
levels(data[,"HoPE_PerfO_VisuoPerc_1"])[!levels(data[,"HoPE_PerfO_VisuoPerc_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_VisuoPerc_2"])[levels(data[,"HoPE_PerfO_VisuoPerc_2"])=="C"]=1
levels(data[,"HoPE_PerfO_VisuoPerc_2"])[!levels(data[,"HoPE_PerfO_VisuoPerc_2"]) %in% c("","1")]=0

#VisuoPerception
levels(data[,"HoPE_PerfO_VisuoSpatial_1"])[levels(data[,"HoPE_PerfO_VisuoSpatial_1"])=="A"]=1
levels(data[,"HoPE_PerfO_VisuoSpatial_1"])[!levels(data[,"HoPE_PerfO_VisuoSpatial_1"]) %in% c("","1")]=0

for(var in HoPE_PerfO){data[,var]=as.numeric(as.character(data[,var]))}

```

### 3. Scale scores. 
```{r ScaleScores}
#Batch1 (FastTest)
data$PRO_SS=apply(data[,HoPE_PRO],1,sum,na.rm=TRUE)
data$PerfO_SS=apply(data[,HoPE_PerfO],1,sum,na.rm=TRUE)

#PHQ2 (REDCap)




```

------------------------------------------------------------------------------------------------------

## **Exploration & Descriptives:**  

### 2. Items. 

####  + PerfO mean score by item. 

```{r PerfOitemmeans}


PerfO_means=round(apply(data[,HoPE_PerfO], 2, mean, na.rm=TRUE),1)
names(PerfO_means)=gsub("HoPE_PerfO_","",HoPE_PerfO)

datatable(cbind("Item"=names(PerfO_means),"Item Mean"=PerfO_means), 
            rownames = FALSE,
            extensions = 'Buttons',
            options = list(
              paging = TRUE,
              dom = 'Bfrltip',
              buttons = c('copy', 'csv', 'excel', 'pdf'),
              columnDefs = list(list(className = 'dt-center', targets = 0:1)),
              pageLength = 2,
              lengthMenu=c(3,5,10,25,50,100))
          )



h=hist(PerfO_means, plot=FALSE)
plot(h, ylim=c(0,max(h$counts)*1.25), main="Performance Item\nItem Means", xlab="Item Mean (0-1)")
text(h$mids, h$counts+(max(h$counts)/10), h$counts)



```

####  +  PerfO item-total correlation. 

```{r PerfOitemtotalcorr}
PerfO_ItemTotalCorr=apply(data[,HoPE_PerfO], 2, function(x){cor(x,data$PerfO_SS, method="pearson", use = "pairwise.complete.obs")})
names(PerfO_ItemTotalCorr)=gsub("HoPE_PerfO_","",names(PerfO_ItemTotalCorr))
PerfO_ItemTotalCorr=round(PerfO_ItemTotalCorr,2)

datatable(cbind("Item Number"=names(PerfO_means),"Item-SS Correlation"=PerfO_means), 
            rownames = FALSE,
            extensions = 'Buttons',
            options = list(
              paging = TRUE,
              dom = 'Bfrltip',
              buttons = c('copy', 'csv', 'excel', 'pdf'),
              columnDefs = list(list(className = 'dt-center', targets = 0:1)),
              pageLength = 2,
              lengthMenu=c(3,5,10,25,50,100)))

h=hist(PerfO_ItemTotalCorr, plot=FALSE)
plot(h, ylim=c(0,max(h$counts)*1.25), main="Performance Item\nItem-Total Correlation", xlab="r (pearson)")
text(h$mids, h$counts+(max(h$counts)/10), h$counts)

```
  
  
####  + Bivariate correlation. 

```{r BivariateCorr}

BVCorrTable=cor(data[,c(HoPE_PRO,HoPE_PerfO)], use="pairwise.complete.obs", method="spearman")

PerfOCorrTable=BVCorrTable[HoPE_PerfO,HoPE_PerfO]

h=hist(PerfOCorrTable[lower.tri(PerfOCorrTable)], plot=FALSE)
plot(h, ylim=c(0,max(h$counts)*1.25), main="Performance Item\nBivariate Correlation Distribution", xlab="r (pearson)")
text(h$mids, h$counts+(max(h$counts)/10), h$counts)


```


### 2. Persons.
####  + Scale scores. 
```{r Person_ScaleScores}

boxplot(data$PerfO_SS, main="PerfO Sum Score Boxplot", ylab="Sum Score")

```
  

####  + Time to complete test. 
```{r TimeUsedTest}

boxplot(X~Group,
  data.frame(
      X=c(data$Time.Used..s./60,
        apply(ResponseTimes[,HoPE_PerfO],1,sum, na.rm=TRUE)/60,
        apply(ResponseTimes[,HoPE_PRO],1,sum, na.rm=TRUE)/60),
          Group=rep(c("Batch1","PerfO_only","PRO_only"),times=c(nrow(data),nrow(ResponseTimes),nrow(ResponseTimes)))),
  ylab="time elapsed, minutes",
  main="Testing Time")

```

####  + Time distribution per items. 
```{r TimeUsedItems}
ResponseTimes=merge(ResponseTimes,data[,c("Test.Code","PRO_SS","PerfO_SS")],by="Test.Code",all.x = TRUE)

#Item
ItemTime=do.call(rbind,lapply(c(HoPE_PerfO), function(item){
    if(grepl("*PRO*",item)){scale="PRO_SS"}
    if(grepl("*PerfO*",item)){scale="PerfO_SS"}
      
      if(!any(is.na(ResponseTimes[,item]))){res <- c(summary(ResponseTimes[,item]),"NA's"=0)}
      else{res <- summary(ResponseTimes[,item])}

      c(
        "Item"=gsub("HoPE_PRO_|HoPE_PerfO_","",item),
        "n"=sum(!is.na(ResponseTimes[,item]),na.rm=TRUE),
        round(res,2),
        "Time-SS_Rho"=round(cor(ResponseTimes[,item],
          ResponseTimes[,scale],method="pearson",use="pairwise.complete.obs"),2))
    }))


datatable(ItemTime,
            extensions = 'Buttons',
            options = list(
              paging = TRUE,
              dom = 'Bfrltip',
              buttons = c('copy', 'csv', 'excel', 'pdf'),
              pageLength = 2,
              lengthMenu=c(3,5,10,25,50,100)))
          

```




####  + Characteristics (Clin/Demo) by scales. 

```{r DTF}
#variables to work across:

Charactertistics=c("Gender","Race.x","AgeBands","Ethnicity.x","Cogn.Impairment.x")


#Scale
DTF=do.call(rbind,lapply(c("PRO_SS","PerfO_SS"),function(scale){
  do.call(rbind,sapply(Charactertistics, function(var){
    out=t(sapply(unique(data[,var]), function(v){
      if(!any(is.na(data[data[,var]==v,scale]))){res <- c(summary(data[data[,var]==v,scale]),"NA's"=0)}
      else{res <- summary(data[data[,var]==v,scale])}
      c(
          "Scale"=scale,
          "Characteristic"=var,
          "Level"=v,
          "n"=sum(data[,var]==v, na.rm = TRUE),
          round(res,2),
          "PRO-PerfO_Rho"=round(cor(data[data[,var]==v,"PRO_SS"],
            data[data[,var]==v,"PerfO_SS"],method="pearson",use="pairwise.complete.obs"),2))}))
      nums=matrix(as.numeric(out[,4:12]),ncol=9)
    out=rbind(out,c(out[1,1:3],round(diff(rbind(apply(nums[nums[,1]>0,],2,min),apply(nums[nums[,1]>0,],2,max))),2)))
    out[nrow(out),3]="MaxDifference"
    out
    }))}))


datatable(DTF[order(DTF[,"Characteristic"]),],
          class = 'cell-border stripe',
          # container =  container,
          rownames = F,
          extensions = c('RowGroup','Buttons'),
          options = list(searching=TRUE,
                         lengthChange = FALSE,
                         info = F,
                         ordering=F,
                         paging=T,
                         dom = 'Bfrltip',
                         buttons = c('copy', 'csv', 'excel', 'pdf'),
                         rowGroup = list(dataSrc=c(1,0)),
                         columnDefs = list(list(visible=FALSE, targets=c(0, 1)),
                                           list(className = 'dt-body-left',
                                                targets = seq(2)),
                                           list(className = 'dt-body-right',
                                                targets = seq(3:11))
                                           ),
                         pageLength = 20,
                         lengthMenu=c(3,5,10,25,50,100)))

```


####  + Characteristics (Clin/Demo) by items.   

```{r DIF}

#Item
DIF=do.call(rbind,lapply(c(HoPE_PRO,HoPE_PerfO), function(item){
  do.call(rbind,lapply(Charactertistics, function(var){
    if(grepl("*PRO*",item)){scale="PRO_SS"}
    if(grepl("*PerfO*",item)){scale="PerfO_SS"}
    out=t(sapply(unique(data[,var]), function(v){
      
      if(!any(is.na(data[data[,var]==v,item]))){res <- c(summary(data[data[,var]==v,item]),"NA's"=0)}
      else{res <- summary(data[data[,var]==v,item])}
      
        c(          
          "Item"=item,
          "Characteristic"=var,
          "Level"=v,
          "n"=sum(data[,var]==v,na.rm=TRUE),
          round(res,2),
          "Item-SS_Rho"=round(cor(data[data[,var]==v,item],
            data[data[,var]==v,scale],method="spearman",use="pairwise.complete.obs"),2))}))
    
          nums=matrix(as.numeric(out[,4:12]),ncol=9)
    out=rbind(out,c(out[1,1:3],round(diff(rbind(apply(nums[nums[,1]>0,],2,min),apply(nums[nums[,1]>0,],2,max))),2)))
    out[nrow(out),3]="MaxDifference"
    out

    }))}))


datatable(DIF[order(DIF[,"Characteristic"]),],
          class = 'cell-border stripe',
          # container =  container,
          rownames = F,
          extensions = c('RowGroup', 'Buttons'),
          options = list(searching=TRUE,
                         lengthChange = FALSE,
                         info = F,
                         ordering=F,
                         paging=T,
                         dom = 'Bfrltip',
                         buttons = c('copy', 'csv', 'excel', 'pdf'),
                         rowGroup = list(dataSrc=c(1,0)),
                         columnDefs = list(list(visible=FALSE, targets=c(0, 1)),
                                           list(className = 'dt-body-left',
                                                targets = seq(2)),
                                           list(className = 'dt-body-right',
                                                targets = seq(3:11))
                                           ),
                         pageLength = 20,
                         lengthMenu=c(3,5,10,25,50,100)))


```

  
### 3. Missing data by item and persons.   

#### + PerfO missing items.  

```{r PerfOMissingData}

PerfO_Missing_Items=apply(data[,HoPE_PerfO], 2, function(x){sum(is.na(x))})
names(PerfO_Missing_Items)=gsub("HoPE_PerfO_","",HoPE_PerfO)
datatable(cbind("Item"=names(PerfO_Missing_Items),"Missing (N)"=PerfO_Missing_Items), 
            rownames = FALSE,
            extensions = 'Buttons',
            options = list(
              paging = TRUE,
              dom = 'Bfrltip',
              buttons = c('copy', 'csv', 'excel', 'pdf'),
              columnDefs = list(list(className = 'dt-center', targets = 0:1)),
              pageLength = 2,
              lengthMenu=c(3,5,10,25,50,100)))

PerfO_Missing_Persons=apply(data[,HoPE_PerfO], 1, function(x){sum(is.na(x))})
PerfO_Missing_Persons=table(factor(PerfO_Missing_Persons, levels=c(0:max(PerfO_Missing_Persons))))


b=barplot(PerfO_Missing_Persons, ylim=c(0,max(PerfO_Missing_Persons)*1.25), ylab="# of missing items", main="Number of Items Missing\nby Person")
text(b, PerfO_Missing_Persons+max(PerfO_Missing_Persons)*0.1, PerfO_Missing_Persons)

```




