---
title: "HomeCog Batch1 Weekly Reports"
output:
  html_document:
    code_folding: hide
---

Coding for weekly audit of HomeCog Batch 1 data collection. The purpose of this document is to structure what will be circulated and reviewed by the HoPE Aim 1 team on a weekly basis. 

To-Do

ask coordinators about REDCap 'enrollment' variable <- should only ever by '1' correct?

produce PerfO item table
closeout FAMCATS
integrate REDCap into data descriptives and cleaning
integrate qualitative (Notes) data into descriptives
get tracking over time working
look into missing data <- write person-level and item-level reports
integrate into slide set


```{r setup, include=FALSE}
#install.packages("data.table")
library(data.table)
#install.packages("DT")
library(DT)

knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

## **Loading Data:**
```{r loadExcel}
setwd( "/Users/chapm564/Documents/GitHub/HomeCog_Batch1_Weekly_Reports")

#Item Text
item_text=read.csv("~/Documents/GitHub/HomeCog_Batch1_Weekly_Reports/ItemText/Batch_1_Item_Text.csv")

#HoPE Calibration Recruitment
Recruitment=read.delim("HoPe Calibration - All Patients.txt",sep="\t")
names(Recruitment)[names(Recruitment)=="Participant.ID"]="Recruitment_id"
names(Recruitment)[names(Recruitment)=="FastTest.ID"]="Test.Code"
names(Recruitment)[names(Recruitment)=="Age"]="Recruitment_age"
names(Recruitment)[names(Recruitment)=="Sex"]="Recruitment_gender"

#REDCap data
REDCap=read.csv("ProjectHoPeCalibrati_DATA_2023-12-15_1129.csv")
names(REDCap)[names(REDCap)=="record_id"]="REDCap_id"
names(REDCap)[names(REDCap)=="fasttest"]="Test.Code"
names(REDCap)[names(REDCap)=="enrollment_date"]="REDCap_date"
names(REDCap)[names(REDCap)=="age"]="REDCap_age"
names(REDCap)[names(REDCap)=="gender"]="REDCap_gender"
REDCap$REDCap_gender[REDCap$REDCap_gender==1]="F"
REDCap$REDCap_gender[REDCap$REDCap_gender==2]="M"
REDCap$REDCap_date=strftime(REDCap$REDCap_date, "%m/%d/%Y")


# 
# record_id	<- REDCap ID- rename
# enrollment <- 1/0? maybe remove if not 1
# enrollment_date <- date of adminsitration, check against FastTest date
# fasttest <- merge
# age <- check against Recruitment spreadsheet
# gender <- check against Recruitment spreadsheet
# interest <- PHQ2?
# feeling <- PHQ2?
# within_year <- SDOH questions answered within a year
# alcohol <- SDOH1
# dentist <- SDOH2
# employment <- SDOH3
# inactive <- SDOH3a
# active <- SDOH3b
# olive_oil <- SDOH4
# exercise <- SDOH5
# minutes <- SDOH6
# telephone <- SDOH7
# transportation <- SDOH8
# basics <- ????
# who <- Description of who's answering CareGiving questions below 
# return_you <- CG1a
# return_care <- CG1b
# help_you <- CG2a
# help_care <- CG2b
# hours_you <- CG3a
# hours_care <- CG3b
# limit_care <- CG4
# yes___1 <- CG4a
# yes___2 <- CG4b
# limit_you <- CG5
# yes_you___1 <- CG5a
# yes_you___2 <- CG5b
# comfort_you <- CG6a
# comfort_care <- CG6b
# meds_you <- CG7a
# meds_care <- CG7b
# form_1_complete <- ????


#Read in FastTest Raw Response Data
FastTest=read.csv("ExamineeResponses-12-19-2023-8-59-11.csv", skip = 1, stringsAsFactors = TRUE)
FastTest=FastTest[FastTest$Test=="Batch_1",]
#Remove variables that will be unused for analyses
FastTest=FastTest[,!(names(FastTest) %in% c("Test.Code.Email.s.","Test.Results.Email.s.","External.ID","SE","Passed"))]
#relabel date as FastTest date
names(FastTest)[names(FastTest)=="Date"]="FastTest_date"
FastTest$FastTest_date=as.character(FastTest$FastTest_date)
FastTest$Test.Code=as.character(FastTest$Test.Code)

#Relabel variables from FAMCAT with "FAMCAT_" prefix
FAMCAT=grep("^X[0-9]+[0-9]+[0-9]", names(FastTest))
names(FastTest)[FAMCAT]=gsub("X","FAMCAT_",names(FastTest)[FAMCAT])

#Relabel variables from HoPE Batch 1 PRO items with "HoPE_PRO_" prefix
HoPE_PRO=grep("^X[0-9]+[0-9]|^X[0-9]", names(FastTest), value=TRUE)
names(FastTest)[names(FastTest) %in% HoPE_PRO]=gsub("X","HoPE_PRO_",names(FastTest)[names(FastTest) %in% HoPE_PRO])
HoPE_PRO=gsub("X","HoPE_PRO_",HoPE_PRO)

#Relabel variables from HoPE Batch 1 PerfO items with "HoPE_PerfO_" prefix
HoPE_PerfO=grep("^Memory_|^Naming_|^Semantic_Assoc_|^Comprehension_|^Vigilance_|^Abstraction_|^Sequencing_|^ZChI|^Cc5g|^Uu16|^Arithmetic_|^Clock_|^VisuoPerc_|^VisuoSpatial_" , names(FastTest), value=TRUE)
names(FastTest)[names(FastTest) %in% HoPE_PerfO]=paste0("HoPE_PerfO_",names(FastTest)[names(FastTest) %in% HoPE_PerfO])
HoPE_PerfO=paste0("HoPE_PerfO_",HoPE_PerfO)

#Reduce Batch 1 PRO 'item text' table to only those items administered in Batch 1 (36 items)
item_text=item_text[item_text$Item_Number %in% gsub("HoPE_PRO_","",HoPE_PRO),]

###############################
### load in FAMCAT Scale Scores
###############################

FastTest2=read.csv("ExamineeData-12-19-2023-8-59-01.csv")
FastTest2=FastTest2[FastTest2$Test=="Male"|FastTest2$Test=="Female"& !is.na(FastTest2$First.Name),]


###############################
### load in FAMCAT Scale Scores
###############################

ResponseTimes=read.csv("ItemTimes-12-19-2023-8-59-21.csv")

ResponseTimes=ResponseTimes[ResponseTimes$Test=="Batch_1",]
#Remove variables that will be unused for analyses
ResponseTimes=ResponseTimes[,!(names(ResponseTimes) %in% c("Test.Code.Email.s.","Test.Results.Email.s.","External.ID","SE","Passed"))]
#relabel date as FastTest date
names(ResponseTimes)[names(ResponseTimes)=="Date"]="FastTest_date"

#Relabel variables from FAMCAT with "FAMCAT_" prefix
FAMCATxnames=grep("^X[0-9]+[0-9]+[0-9]", names(ResponseTimes))
names(ResponseTimes)[FAMCATxnames]=gsub("X","FAMCAT_",names(ResponseTimes)[FAMCATxnames])

#Relabel variables from HoPE Batch 1 PRO items with "HoPE_PRO_" prefix
HoPE_PROxnames=grep("^X[0-9]+[0-9]|^X[0-9]", names(ResponseTimes), value=TRUE)
names(ResponseTimes)[names(ResponseTimes) %in% HoPE_PROxnames]=gsub("X","HoPE_PRO_",names(ResponseTimes)[names(ResponseTimes) %in% HoPE_PROxnames])


#Relabel variables from HoPE Batch 1 PerfO items with "HoPE_PerfO_" prefix
HoPE_PerfOxnames=grep("^Memory_|^Naming_|^Semantic_Assoc_|^Comprehension_|^Vigilance_|^Abstraction_|^Sequencing_|^ZChI|^Cc5g|^Uu16|^Arithmetic_|^Clock_|^VisuoPerc_|^VisuoSpatial_" , names(ResponseTimes), value=TRUE)
names(ResponseTimes)[names(ResponseTimes) %in% HoPE_PerfOxnames]=paste0("HoPE_PerfO_",names(ResponseTimes)[names(ResponseTimes) %in% HoPE_PerfOxnames])

```

```{r DataLinking}

#Adjustments to be relayed to coordinators 
REDCap[REDCap$Test.Code=="MIH-090-764-944", "REDCap_date"]="11/30/2023"
REDCap[REDCap$Test.Code=="ECO-622-460-859", "REDCap_gender"]="F"
FastTest=FastTest[!(FastTest$Test.Code %in% c("CBU-218-600-873","NYS-954-156-833")),]
FastTest2=FastTest2[!(FastTest2$Test.Code %in% c("CBU-218-600-873","NYS-954-156-833")),]


# Administration Date Linking
MergeCheck=merge(FastTest, REDCap, by="Test.Code")
if(length(which(MergeCheck$FastTest_date != MergeCheck$REDCap_date))==0){
    names(FastTest)[names(FastTest)=="FastTest_date"]="Date"
    names(REDCap)[names(REDCap)=="REDCap_date"]="Date"
}else{print(paste("DATE MISMATCH: FastTest & REDCap"))}

# ID Linking
MergeCheck=merge(Recruitment, REDCap, by="Test.Code")
if(length(which(MergeCheck$Recruitment_id != MergeCheck$REDCap_id))==0){
    names(Recruitment)[names(Recruitment)=="Recruitment_id"]="ID"
    names(REDCap)[names(REDCap)=="REDCap_id"]="ID"
  }else{print("ID MISMATCH: Recruitment & REDCap")}

# Age
if(length(which(as.numeric(gsub("-year old", "",MergeCheck$Recruitment_age)) != MergeCheck$REDCap_age))==0){
    names(Recruitment)[names(Recruitment)=="Recruitment_id"]="ID"
    names(REDCap)[names(REDCap)=="REDCap_id"]="ID"
  }else{print("AGE MISMATCH: Recruitment & REDCap")}

# Gender
if(length(which(MergeCheck$Recruitment_gender != MergeCheck$REDCap_gender))==0){
    names(Recruitment)[names(Recruitment)=="Recruitment_gender"]="Gender"
    names(REDCap)[names(REDCap)=="REDCap_gender"]="Gender"
  }else{print("GENDER MISMATCH: Recruitment & REDCap")}


###############################################
### Merge #####################################
###############################################
#Merge together FastTest Batch 1 and FastTest Non-Porch FAMCAT
data=merge(by = "Test.Code", all.x=TRUE,
  x=FastTest,
  y=FastTest2[,c("Test.Code",sapply(c("APPLIED_COGNITION","DAILY_ACTIVITIES","MOBILITY"), paste0, c("_SCORE","_SEM")))])
#Merge together FastTest (Batch1 & FAMCAT NonPorch) with Recruitment data
data=merge(by = "Test.Code", all.x=TRUE,
  x=data,
  y=Recruitment)
#Merge together FastTest (Batch1 & FAMCAT NonPorch) & Recruitment data with REDCap data
data=merge(by = "Test.Code", all.x=TRUE,
  x=data,
  y=REDCap)

```

### PRO item text/content domains
`r datatable(item_text, rownames=FALSE, options = list(
  columnDefs = list(list(className = 'dt-center', targets = 0)),
  pageLength = 2))`

------------------------------------------------------------------------------------------------------

## **Manipulation:**  

### 1. Create variable for ‘impaired cognition’ flag (</>= -1.5 AC). 
```{r SafetyFlag}
#FAMCAT AC Safety Flag (< -1.5 AC)
data$AC_Flag= data$APPLIED_COGNITION_SCORE< -1.5
```

### 2. Create variable for group membership. 
```{r GroupMembership, eval=FALSE}

#Group1 - those with ADRD diagnoses
data$Group1= data$ADRD != 0

#Group2 - those without ADRD diagnosis but FAMCAT AC < -1.5
data$Group2= (data$ADRD == 0 & data$AC_Flag)

#Group3 - those without ADRD and FAMCAT AC >=-1.5
data$Group3= (data$ADRD == 0 & !data$AC_Flag)

```

------------------------------------------------------------------------------------------------------

## **Data Cleaning.** 
  
### 0. Data recoding.  
```{r Recoding, results='hide'}

#####Recruitment

#need to reduce down the dataset to just the folks with FastTest data or just those with data for recruitment

#Gender
table(Recruitment$Recruitment_gender)
#Race <- 15 folks missing or ""
table(Recruitment$Race)
#Ethnicity <- 15 folks missing or ""
table(Recruitment$Ethnicity)
#Age 
Recruitment$Recruitment_age=as.numeric(gsub("-year old","",Recruitment$Recruitment_age))
table(Recruitment$Recruitment_age)
#Age bands (<65 & >=65)
Recruitment$AgeBands=as.character(cut(as.numeric(Recruitment$Recruitment_age), breaks=c(0,65,120), right=FALSE))
data$AgeBands=cut(data$REDCap_age, breaks=c(0,65,120), right=FALSE)
#Cognitive impairment
table(Recruitment$Cogn.Impairment)

#HomeCog Status
table(Recruitment$HomeCog.Interrupted....completed..)

#FAMCAT Status
table(Recruitment$FAMCAT.Interrupted....completed..)

#Audio
table(Recruitment$Audio..Good.Bad.)

#Notes
table(Recruitment$Notes)

#####FastTest PRO
for(var in HoPE_PRO){
  levels(data[,var])[which(levels(data[,var])=="")]=NA
  
  levels(data[,var])[which(levels(data[,var])=="Very Often")]=1
  levels(data[,var])[which(levels(data[,var])=="Often")]=2
  levels(data[,var])[which(levels(data[,var])=="Sometimes")]=3
  levels(data[,var])[which(levels(data[,var])=="Rarely")]=4
  levels(data[,var])[which(levels(data[,var])=="Never")]=5  
  
  levels(data[,var])[which(levels(data[,var])=="Unable")]=1
  levels(data[,var])[which(levels(data[,var])=="A lot")]=2
  levels(data[,var])[which(levels(data[,var])=="Some")]=3
  levels(data[,var])[which(levels(data[,var])=="A little")]=4  
  levels(data[,var])[which(levels(data[,var])=="None")]=5
  data[,var]=as.numeric(data[,var])
}


#FastTest PerfO

for(var in HoPE_PerfO){data[,var]=as.factor(data[,var])}

#Memory
levels(data[,"HoPE_PerfO_Memory_1"])[levels(data[,"HoPE_PerfO_Memory_1"])=="B"]=1
levels(data[,"HoPE_PerfO_Memory_1"])[!levels(data[,"HoPE_PerfO_Memory_1"]) %in% c("","1")]=0
  
levels(data[,"HoPE_PerfO_Memory_2"])[levels(data[,"HoPE_PerfO_Memory_2"])=="A"]=1
levels(data[,"HoPE_PerfO_Memory_2"])[!levels(data[,"HoPE_PerfO_Memory_2"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Memory_3"])[levels(data[,"HoPE_PerfO_Memory_3"])=="D"]=1
levels(data[,"HoPE_PerfO_Memory_3"])[!levels(data[,"HoPE_PerfO_Memory_3"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Memory_4"])[levels(data[,"HoPE_PerfO_Memory_4"])=="C"]=1
levels(data[,"HoPE_PerfO_Memory_4"])[!levels(data[,"HoPE_PerfO_Memory_4"]) %in% c("","1")]=0

#Naming
levels(data[,"HoPE_PerfO_Naming_1"])[levels(data[,"HoPE_PerfO_Naming_1"])=="D"]=1
levels(data[,"HoPE_PerfO_Naming_1"])[!levels(data[,"HoPE_PerfO_Naming_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Naming_2"])[levels(data[,"HoPE_PerfO_Naming_2"])=="A"]=1
levels(data[,"HoPE_PerfO_Naming_2"])[!levels(data[,"HoPE_PerfO_Naming_2"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Naming_3"])[levels(data[,"HoPE_PerfO_Naming_3"])=="B"]=1
levels(data[,"HoPE_PerfO_Naming_3"])[!levels(data[,"HoPE_PerfO_Naming_3"]) %in% c("","1")]=0

#Semantic Association
levels(data[,"HoPE_PerfO_Semantic_Assoc_1"])[levels(data[,"HoPE_PerfO_Semantic_Assoc_1"])=="C"]=1
levels(data[,"HoPE_PerfO_Semantic_Assoc_1"])[!levels(data[,"HoPE_PerfO_Semantic_Assoc_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Semantic_Assoc_2"])[levels(data[,"HoPE_PerfO_Semantic_Assoc_2"])=="D"]=1
levels(data[,"HoPE_PerfO_Semantic_Assoc_2"])[!levels(data[,"HoPE_PerfO_Semantic_Assoc_2"]) %in% c("","1")]=0


#Comprehension
levels(data[,"HoPE_PerfO_Comprehension_1"])[levels(data[,"HoPE_PerfO_Comprehension_1"])=="B"]=1
levels(data[,"HoPE_PerfO_Comprehension_1"])[!levels(data[,"HoPE_PerfO_Comprehension_1"]) %in% c("","1")]=0

#Vigilance
levels(data[,"HoPE_PerfO_Vigilance_1"])[levels(data[,"HoPE_PerfO_Vigilance_1"])=="C"]=1
levels(data[,"HoPE_PerfO_Vigilance_1"])[!levels(data[,"HoPE_PerfO_Vigilance_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Vigilance_2"])[levels(data[,"HoPE_PerfO_Vigilance_2"])=="C"]=1
levels(data[,"HoPE_PerfO_Vigilance_2"])[!levels(data[,"HoPE_PerfO_Vigilance_2"]) %in% c("","1")]=0

#Abstraction
levels(data[,"HoPE_PerfO_Abstraction_1"])[levels(data[,"HoPE_PerfO_Abstraction_1"])=="B"]=1
levels(data[,"HoPE_PerfO_Abstraction_1"])[!levels(data[,"HoPE_PerfO_Abstraction_1"]) %in% c("","1")]=0

#Sequencing - this might take some work
levels(data[,"HoPE_PerfO_ZChI"])[levels(data[,"HoPE_PerfO_ZChI"])=="E"]=1
levels(data[,"HoPE_PerfO_ZChI"])[!levels(data[,"HoPE_PerfO_ZChI"]) %in% c("","1")]=0
data[,"HoPE_PerfO_Sequencing_1"]=data[,"HoPE_PerfO_ZChI"]
data=data[,-which(names(data)=="HoPE_PerfO_ZChI")]
HoPE_PerfO=HoPE_PerfO[-which(HoPE_PerfO=="HoPE_PerfO_ZChI")]

levels(data[,"HoPE_PerfO_Cc5g"])[levels(data[,"HoPE_PerfO_Cc5g"])=="20"]=1
levels(data[,"HoPE_PerfO_Cc5g"])[!levels(data[,"HoPE_PerfO_Cc5g"]) %in% c("","1")]=0
data[,"HoPE_PerfO_Sequencing_2"]=data[,"HoPE_PerfO_Cc5g"]
data=data[,-which(names(data)=="HoPE_PerfO_Cc5g")]
HoPE_PerfO=HoPE_PerfO[-which(HoPE_PerfO=="HoPE_PerfO_Cc5g")]

levels(data[,"HoPE_PerfO_Uu16"])[levels(data[,"HoPE_PerfO_Uu16"])=="72"]=1
levels(data[,"HoPE_PerfO_Uu16"])[!levels(data[,"HoPE_PerfO_Uu16"]) %in% c("","1")]=0
data[,"HoPE_PerfO_Sequencing_3"]=data[,"HoPE_PerfO_Uu16"]
data=data[,-which(names(data)=="HoPE_PerfO_Uu16")]
HoPE_PerfO=HoPE_PerfO[-which(HoPE_PerfO=="HoPE_PerfO_Uu16")]

#Arithmetic
levels(data[,"HoPE_PerfO_Arithmetic_1"])[levels(data[,"HoPE_PerfO_Arithmetic_1"])=="A"]=1
levels(data[,"HoPE_PerfO_Arithmetic_1"])[!levels(data[,"HoPE_PerfO_Arithmetic_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_2"])[levels(data[,"HoPE_PerfO_Arithmetic_2"])=="C"]=1
levels(data[,"HoPE_PerfO_Arithmetic_2"])[!levels(data[,"HoPE_PerfO_Arithmetic_2"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_3"])[levels(data[,"HoPE_PerfO_Arithmetic_3"])=="B"]=1
levels(data[,"HoPE_PerfO_Arithmetic_3"])[!levels(data[,"HoPE_PerfO_Arithmetic_3"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_4"])[levels(data[,"HoPE_PerfO_Arithmetic_4"])=="A"]=1
levels(data[,"HoPE_PerfO_Arithmetic_4"])[!levels(data[,"HoPE_PerfO_Arithmetic_4"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_5"])[levels(data[,"HoPE_PerfO_Arithmetic_5"])=="B"]=1
levels(data[,"HoPE_PerfO_Arithmetic_5"])[!levels(data[,"HoPE_PerfO_Arithmetic_5"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_6"])[levels(data[,"HoPE_PerfO_Arithmetic_6"])=="B"]=1
levels(data[,"HoPE_PerfO_Arithmetic_6"])[!levels(data[,"HoPE_PerfO_Arithmetic_6"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_7"])[levels(data[,"HoPE_PerfO_Arithmetic_7"])=="C"]=1
levels(data[,"HoPE_PerfO_Arithmetic_7"])[!levels(data[,"HoPE_PerfO_Arithmetic_7"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Arithmetic_8"])[levels(data[,"HoPE_PerfO_Arithmetic_8"])=="A"]=1
levels(data[,"HoPE_PerfO_Arithmetic_8"])[!levels(data[,"HoPE_PerfO_Arithmetic_8"]) %in% c("","1")]=0

#Clock
levels(data[,"HoPE_PerfO_Clock_1"])[levels(data[,"HoPE_PerfO_Clock_1"])=="A"]=1
levels(data[,"HoPE_PerfO_Clock_1"])[!levels(data[,"HoPE_PerfO_Clock_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_Clock_2"])[levels(data[,"HoPE_PerfO_Clock_2"])=="B"]=1
levels(data[,"HoPE_PerfO_Clock_2"])[!levels(data[,"HoPE_PerfO_Clock_2"]) %in% c("","1")]=0

#VisuoPerception
levels(data[,"HoPE_PerfO_VisuoPerc_1"])[levels(data[,"HoPE_PerfO_VisuoPerc_1"])=="D"]=1
levels(data[,"HoPE_PerfO_VisuoPerc_1"])[!levels(data[,"HoPE_PerfO_VisuoPerc_1"]) %in% c("","1")]=0

levels(data[,"HoPE_PerfO_VisuoPerc_2"])[levels(data[,"HoPE_PerfO_VisuoPerc_2"])=="C"]=1
levels(data[,"HoPE_PerfO_VisuoPerc_2"])[!levels(data[,"HoPE_PerfO_VisuoPerc_2"]) %in% c("","1")]=0

#VisuoPerception
levels(data[,"HoPE_PerfO_VisuoSpatial_1"])[levels(data[,"HoPE_PerfO_VisuoSpatial_1"])=="A"]=1
levels(data[,"HoPE_PerfO_VisuoSpatial_1"])[!levels(data[,"HoPE_PerfO_VisuoSpatial_1"]) %in% c("","1")]=0

for(var in HoPE_PerfO){data[,var]=as.numeric(as.character(data[,var]))}

```

### 1. Out of range data. 
```{r OutOfRange}

#FastTest
data$PRO_OOR_Flag=apply(data[,HoPE_PRO],1,function(r){!any(r %in% c(1:5,NA))})
data$PerfO_OOR_Flag=apply(data[,HoPE_PerfO],1,function(r){!any(r %in% c(0:1,NA))})


```

### 2. Unique values.
```{r UniqueValues}
#PROs
cat("PRO Unique Values:", unique(c(unlist(apply(data[,HoPE_PRO], 2, unique)))))

#PerfOs
cat("PerfO Unique Values:",unique(c(unlist(apply(data[,HoPE_PerfO], 2, unique)))))

#REDCap
table(REDCap$enrollment) #<- Should only be zero, ask coordinators?


```

### 3. Scale scores. 
```{r ScaleScores}
#Batch1 (FastTest)
data$PRO_SS=apply(data[,HoPE_PRO],1,sum,na.rm=TRUE)
data$PerfO_SS=apply(data[,HoPE_PerfO],1,sum,na.rm=TRUE)

#PHQ2 (REDCap)




```

------------------------------------------------------------------------------------------------------

## **Exploration & Descriptives:**  
### 1. Recruitment Targets. 
####  + Clinical Characteristics/Demographic breakdown (with targets). 
```{r RecruitTargets}
#ADRD diag & those without ADRD diag but <-1.5 AC
#table(data$AC_Flag,data$ADRD)
#gender should be 50% female
round(prop.table(table(data$Sex)),2)
```
  
####  + Coordinator/administrator notes. 

```{r CoordNotes, results='hide'}

table(data$Notes[which(data$Notes!="")])

```


### 2. Items. 
####  + PRO Frequency (N/Proportion) response tables.
```{r PROFreqRespTable}

PROFreqTable=apply(data[,HoPE_PRO], 2, function(x){x=as.factor(x);levels(x)=1:5;table(x);})
colnames(PROFreqTable)=gsub("HoPE_PRO_","",colnames(PROFreqTable))
PROFreqTable=cbind(PROFreqTable,"Total"=rowSums(PROFreqTable))
datatable(t(PROFreqTable),
            colnames = c('Item' = 1),
            options = list(
              columnDefs = list(list(className = 'dt-center', targets = 0:5)),
              pageLength = 2))

PROPropFreqTable=round(prop.table(PROFreqTable, margin=2)*100,2)
datatable(t(PROPropFreqTable),
            colnames = c('Item' = 1),
            options = list(
              columnDefs = list(list(className = 'dt-center', targets = 0:5)),
              pageLength = 2))


```
  
  
####  + PRO mean score by item. 
  
```{r PROitemmeans}

PRO_means=round(apply(data[,HoPE_PRO], 2, mean, na.rm=TRUE),1)
names(PRO_means)=gsub("HoPE_PRO_","",HoPE_PRO)


datatable(cbind("Item"=names(PRO_means),"Item Mean"=PRO_means), 
            rownames = FALSE,
            extensions = 'Buttons',
            options = list(
              paging = TRUE,
              dom = 'Bfrltip',
              buttons = c('copy', 'csv', 'excel', 'pdf'),
              columnDefs = list(list(className = 'dt-center', targets = 0:1)),
              pageLength = 2,
              lengthMenu=c(3,5,10,25,50,100))
          )



h=hist(PRO_means, plot=FALSE)
plot(h, xlim=c(1,5), ylim=c(0,max(h$counts)*1.25), main="PRO Item\nItem Means", xlab="Item Mean (1-5)")
text(h$mids, h$counts+(max(h$counts)/10), h$counts)


```


####  + PerfO mean score by item. 

```{r PerfOitemmeans}

PerfO_means=round(apply(data[,HoPE_PerfO], 2, mean, na.rm=TRUE),1)
names(PerfO_means)=gsub("HoPE_PerfO_","",HoPE_PerfO)

datatable(cbind("Item"=names(PerfO_means),"Item Mean"=PerfO_means), 
            rownames = FALSE,
            extensions = 'Buttons',
            options = list(
              paging = TRUE,
              dom = 'Bfrltip',
              buttons = c('copy', 'csv', 'excel', 'pdf'),
              columnDefs = list(list(className = 'dt-center', targets = 0:1)),
              pageLength = 2,
              lengthMenu=c(3,5,10,25,50,100))
          )



h=hist(PerfO_means, plot=FALSE)
plot(h, ylim=c(0,max(h$counts)*1.25), main="Performance Item\nItem Means", xlab="Item Mean (0-1)")
text(h$mids, h$counts+(max(h$counts)/10), h$counts)

```

####  +  PRO item-total correlation. 

```{r PROitemtotalcorr}

PRO_ItemTotalCorr=apply(data[,HoPE_PRO], 2, function(x){cor(x,data$PRO_SS, method="spearman", use = "pairwise.complete.obs")})
names(PRO_ItemTotalCorr)=gsub("HoPE_PRO_","",names(PRO_ItemTotalCorr))
PRO_ItemTotalCorr=round(PRO_ItemTotalCorr,2)

datatable(cbind("Item Number"=names(PRO_ItemTotalCorr),"Item-SS Correlation"=PRO_ItemTotalCorr), 
            rownames = FALSE,
            extensions = 'Buttons',
            options = list(
              paging = TRUE,
              dom = 'Bfrltip',
              buttons = c('copy', 'csv', 'excel', 'pdf'),
              columnDefs = list(list(className = 'dt-center', targets = 0:1)),
              pageLength = 2,
              lengthMenu=c(3,5,10,25,50,100)))

h=hist(PRO_ItemTotalCorr, plot=FALSE)
plot(h, ylim=c(0,max(h$counts)*1.25), main="PRO Item\nItem-Total Correlation", xlab="r (spearman)")
text(h$mids, h$counts+(max(h$counts)/10), h$counts)





```


####  +  PerfO item-total correlation. 

```{r PerfOitemtotalcorr}
PerfO_ItemTotalCorr=apply(data[,HoPE_PerfO], 2, function(x){cor(x,data$PerfO_SS, method="spearman", use = "pairwise.complete.obs")})
names(PerfO_ItemTotalCorr)=gsub("HoPE_PerfO_","",names(PerfO_ItemTotalCorr))
PerfO_ItemTotalCorr=round(PerfO_ItemTotalCorr,2)

datatable(cbind("Item Number"=names(PerfO_ItemTotalCorr),"Item-SS Correlation"=PerfO_ItemTotalCorr), 
            rownames = FALSE,
            extensions = 'Buttons',
            options = list(
              paging = TRUE,
              dom = 'Bfrltip',
              buttons = c('copy', 'csv', 'excel', 'pdf'),
              columnDefs = list(list(className = 'dt-center', targets = 0:1)),
              pageLength = 2,
              lengthMenu=c(3,5,10,25,50,100)))

h=hist(PerfO_ItemTotalCorr, plot=FALSE)
plot(h, ylim=c(0,max(h$counts)*1.25), main="Performance Item\nItem-Total Correlation", xlab="r (spearman)")
text(h$mids, h$counts+(max(h$counts)/10), h$counts)


```
  
  
####  + Bivariate correlation. 

```{r BivariateCorr}

BVCorrTable=cor(data[,c(HoPE_PRO,HoPE_PerfO)], use="pairwise.complete.obs", method="spearman")


h=hist(BVCorrTable[lower.tri(BVCorrTable)], plot=FALSE)
plot(h, ylim=c(0,max(h$counts)*1.25), main="Batch 1 (PRO & PerfO)\nBivariate Correlation Distribution", xlab="r (spearman)")
text(h$mids, h$counts+(max(h$counts)/10), h$counts)

PROCorrTable=BVCorrTable[HoPE_PRO,HoPE_PRO]

PerfOCorrTable=BVCorrTable[HoPE_PerfO,HoPE_PerfO]

h=hist(PerfOCorrTable[lower.tri(PerfOCorrTable)], plot=FALSE)
plot(h, ylim=c(0,max(h$counts)*1.25), main="Performance Item\nBivariate Correlation Distribution", xlab="r (spearman)")
text(h$mids, h$counts+(max(h$counts)/10), h$counts)

h=hist(PROCorrTable[lower.tri(PROCorrTable)], plot=FALSE)
plot(h, ylim=c(0,max(h$counts)*1.25), main="PRO Item\nBivariate Correlation Distribution", xlab="r (spearman)")
text(h$mids, h$counts+(max(h$counts)/10), h$counts)




```


### 2. Persons.
####  + Scale scores. 
```{r Person_ScaleScores}

boxplot(data$PRO_SS, ylim=c(length(HoPE_PRO),length(HoPE_PRO)*5), main="PRO Sum Score Boxplot")

boxplot(data$PerfO_SS, ylim=c(length(HoPE_PerfO)*0,length(HoPE_PerfO)), main="PerfO Sum Score Boxplot")

```
  
####  + Time to complete test. 
```{r TimeUsedTest}

boxplot(X~Group,
  data.frame(
      X=c(data$Time.Used..s./60,
        apply(ResponseTimes[,HoPE_PerfO],1,sum, na.rm=TRUE)/60,
        apply(ResponseTimes[,HoPE_PRO],1,sum, na.rm=TRUE)/60),
          Group=rep(c("Batch1","PerfO_only","PRO_only"),times=c(nrow(data),nrow(ResponseTimes),nrow(ResponseTimes)))),
  ylab="time elapsed, minutes",
  main="Testing Time")

```

####  + Time distribution per items. 
```{r TimeUsedItems}
ResponseTimes=merge(ResponseTimes,data[,c("Test.Code","PRO_SS","PerfO_SS")],by="Test.Code",all.x = TRUE)

#Item
ItemTime=do.call(rbind,lapply(c(HoPE_PerfO), function(item){
    if(grepl("*PRO*",item)){scale="PRO_SS"}
    if(grepl("*PerfO*",item)){scale="PerfO_SS"}
      
      if(!any(is.na(ResponseTimes[,item]))){res <- c(summary(ResponseTimes[,item]),"NA's"=0)}
      else{res <- summary(ResponseTimes[,item])}

      c(
        "Item"=gsub("HoPE_PRO_|HoPE_PerfO_","",item),
        "n"=sum(!is.na(ResponseTimes[,item]),na.rm=TRUE),
        round(res,2),
        "Time-SS_Rho"=round(cor(ResponseTimes[,item],
          ResponseTimes[,scale],method="pearson",use="pairwise.complete.obs"),2))
    }))


datatable(ItemTime,
            extensions = 'Buttons',
            options = list(
              paging = TRUE,
              dom = 'Bfrltip',
              buttons = c('copy', 'csv', 'excel', 'pdf'),
              pageLength = 2,
              lengthMenu=c(3,5,10,25,50,100)))
          

```


####  + Characteristics (Clin/Demo) by scales. 

```{r DTF}
#variables to work across:

Charactertistics=c("Gender.x","Race","AgeBands","Ethnicity","Cogn.Impairment")


#Scale
DTF=do.call(rbind,lapply(c("PRO_SS","PerfO_SS"),function(scale){
  do.call(rbind,sapply(Charactertistics, function(var){
    out=t(sapply(unique(data[,var]), function(v){
      if(!any(is.na(data[data[,var]==v,scale]))){res <- c(summary(data[data[,var]==v,scale]),"NA's"=0)}
      else{res <- summary(data[data[,var]==v,scale])}
      c(
          "Scale"=scale,
          "Characteristic"=var,
          "Level"=v,
          "n"=sum(data[,var]==v, na.rm = TRUE),
          round(res,2),
          "PRO-PerfO_Rho"=round(cor(data[data[,var]==v,"PRO_SS"],
            data[data[,var]==v,"PerfO_SS"],method="pearson",use="pairwise.complete.obs"),2))}))
      nums=matrix(as.numeric(out[,4:12]),ncol=9)
    out=rbind(out,c(out[1,1:3],round(diff(rbind(apply(nums[nums[,1]>0,],2,min),apply(nums[nums[,1]>0,],2,max))),2)))
    out[nrow(out),3]="MaxDifference"
    out
    }))}))


datatable(DTF[order(DTF[,"Characteristic"]),],
          class = 'cell-border stripe',
          # container =  container,
          rownames = F,
          extensions = c('RowGroup','Buttons'),
          options = list(searching=TRUE,
                         lengthChange = FALSE,
                         info = F,
                         ordering=F,
                         paging=T,
                         dom = 'Bfrltip',
                         buttons = c('copy', 'csv', 'excel', 'pdf'),
                         rowGroup = list(dataSrc=c(1,0)),
                         columnDefs = list(list(visible=FALSE, targets=c(0, 1)),
                                           list(className = 'dt-body-left',
                                                targets = seq(2)),
                                           list(className = 'dt-body-right',
                                                targets = seq(3:11))
                                           ),
                         pageLength = 20,
                         lengthMenu=c(3,5,10,25,50,100)))

```


####  + Characteristics (Clin/Demo) by items.   

```{r DIF}

#Item
DIF=do.call(rbind,lapply(c(HoPE_PRO,HoPE_PerfO), function(item){
  do.call(rbind,lapply(Charactertistics, function(var){
    if(grepl("*PRO*",item)){scale="PRO_SS"}
    if(grepl("*PerfO*",item)){scale="PerfO_SS"}
    out=t(sapply(unique(data[,var]), function(v){
      
      if(!any(is.na(data[data[,var]==v,item]))){res <- c(summary(data[data[,var]==v,item]),"NA's"=0)}
      else{res <- summary(data[data[,var]==v,item])}
      
        c(          
          "Item"=item,
          "Characteristic"=var,
          "Level"=v,
          "n"=sum(data[,var]==v,na.rm=TRUE),
          round(res,2),
          "Item-SS_Rho"=round(cor(data[data[,var]==v,item],
            data[data[,var]==v,scale],method="spearman",use="pairwise.complete.obs"),2))}))
    
          nums=matrix(as.numeric(out[,4:12]),ncol=9)
    out=rbind(out,c(out[1,1:3],round(diff(rbind(apply(nums[nums[,1]>0,],2,min),apply(nums[nums[,1]>0,],2,max))),2)))
    out[nrow(out),3]="MaxDifference"
    out

    }))}))


datatable(DIF[order(DIF[,"Characteristic"]),],
          class = 'cell-border stripe',
          # container =  container,
          rownames = F,
          extensions = c('RowGroup', 'Buttons'),
          options = list(searching=TRUE,
                         lengthChange = FALSE,
                         info = F,
                         ordering=F,
                         paging=T,
                         dom = 'Bfrltip',
                         buttons = c('copy', 'csv', 'excel', 'pdf'),
                         rowGroup = list(dataSrc=c(1,0)),
                         columnDefs = list(list(visible=FALSE, targets=c(0, 1)),
                                           list(className = 'dt-body-left',
                                                targets = seq(2)),
                                           list(className = 'dt-body-right',
                                                targets = seq(3:11))
                                           ),
                         pageLength = 20,
                         lengthMenu=c(3,5,10,25,50,100)))


```

  
### 3. Missing data by item and persons.   
#### + PRO missing items.  
```{r PROMissingData}

PRO_Missing=apply(data[,HoPE_PRO], 2, function(x){sum(is.na(x))})
names(PRO_Missing)=gsub("HoPE_PRO_","",HoPE_PRO)
datatable(cbind("Item Number"=names(PRO_Missing),"Missing (N)"=PRO_Missing), rownames = FALSE,
            options = list(
              columnDefs = list(list(className = 'dt-center', targets = 0:1)),
              pageLength = 2))

```


#### + PerfO missing items.  

```{r PerfOMissingData}

PerfO_Missing=apply(data[,HoPE_PerfO], 2, function(x){sum(is.na(x))})
names(PerfO_Missing)=gsub("HoPE_PerfO_","",HoPE_PerfO)
datatable(cbind("Item"=names(PerfO_Missing),"Missing (N)"=PerfO_Missing), rownames = FALSE,
            options = list(
              columnDefs = list(list(className = 'dt-center', targets = 0:1)),
              pageLength = 2))
```

### 4. Track over time. 
  
  
  
### 5. Linking Items. 
```{r LinkingItems}

```






