---
title: "HomeCog Batch1 Weekly Reports"
output: html_notebook
---
Coding for weekly review of HomeCog Batch 1 data collection. The purpose of this document is to structure what will be reviewed on a weekly basis. 

# Load the data (right now simulated). 

```{r DataSim}
PROni=35
PerfOni=35
samplesize=50

PROItems=matrix(sample(1:5,PROni*samplesize,replace=TRUE),nrow=samplesize,ncol=PROni, dimnames = list(c(),paste0("PRO",1:PROni)))
PerfoItems=matrix(sample(c(0,1),PerfOni*samplesize,replace=TRUE),nrow=samplesize,ncol=PerfOni, dimnames=list(c(),paste0("PerfO",1:PerfOni)))

ClinicalCharacteristics=data.frame(
  #ADRD diagnosis (sim 1:5)
  "ADRD"=sample(1:5,samplesize,replace=TRUE),
  #FAMCAT AC
  "FAMCAT_AC"=sample(seq(-3,3,0.1),samplesize,replace=TRUE),
  "FAMCAT_Mob"=sample(seq(-3,3,0.1),samplesize,replace=TRUE),
  "FAMCAT_DA"=sample(seq(-3,3,0.1),samplesize,replace=TRUE))

Demographics=data.frame(
  #age
  "age"=rnorm(samplesize,55,7),
  #gender
  "gender"=sample(c("m","f"),samplesize,replace=TRUE))

data=do.call(cbind, list(Demographics, ClinicalCharacteristics, PROItems, PerfoItems))

```


# Manipulation:  
1. Create variable for group membership. 
```{r GroupMembership}

```

2. Create variable for ‘impaired cognition’ flag (</>= -1.5 AC). 
```{r SafetyFlag}
#FAMCAT AC Safety Flag (<-1.5 AC)
Data$AC_Flag=cut(ClinicalCharacteristics$FAMCAT_AC,breaks=c(-99,-1.5,99),right=FALSE)
```

3. Scale scores. 
  + PRO
```{r PRO_ScaleScores}
data$PRO_SS=apply(data[,grep("^PRO[1-9].*",names(data))],1,sum,na.rm=TRUE)
```

  + PerfO
```{r PerfO_ScaleScores}
data$PerfO_SS=apply(data[,grep("^PerfO[1-9].*",names(data))],1,sum,na.rm=TRUE)
```




# Data Cleaning. 
1. Out of range data. 
```{r OutOfRange}

data$PRO_OOR_Flag=apply(data[,grep("^PRO[1-9]*",names(data))],1,function(r){!any(r %in% 1:5)})

data$PerfO_OOR_Flag=apply(data[,grep("^PRO[1-9]*",names(data))],1,function(r){!any(r %in% 0:1)})

```



# Exploration & Descriptives:  
1. Recruitment Targets. 
  + Clinical Characteristics/Demographic breakdown (with targets). 
```{r RecruitTargets}
#ADRD diag & those without ADRD diag but <-1.5 AC
table(data$AC_Flag,data$ADRD)
#gender should be 50% female
table(data$gender)
```
  
  + Coordinator/administrator notes. 

1. Items. 
  + PRO Freq response tables.
```{r PROFreqRespTable}

PROFreqTable=apply(data[,grep("^PRO[1-9].*",names(data))], 2, table)
PROPropFreqTable=apply(PROFreqTable, 2, prop.table)

```
  
  + Bivariate correlation. 

```{r BivariateCorr}

PROCorrTable=cor(data[,grep("^PRO[1-9].*",names(data))], use="pairwise.complete.obs", method="spearman")

hist(PROCorrTable[lower.tri(PROCorrTable)])

```


2. Persons.
  + Scale scores. 
  + Time distribution per items. 
  + Time to complete test. 
  + Characteristics (Clin/Demo) by items/scales
  
3. Missing data by item and persons. 

4. Track over time. 






